\Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-13 articles/2014/whisper/aricleEbauche/articleIrodsUserMeeting.tex
add references for whisper project

The \emph{Whisper} \footnote{FP7 ERC Advanced grant 227507, see whisper.obs.ujf-grenoble.fr} 
project is a an european project on seismology whose goal is to study properties of the earth
with the seismic ambient noise such that evolution of seismic waves speed. 
This noise is almost all the signal continuously recorded by
the seismic stations worldwide (Europe, China, USA, Japan), except earthquakes. It offers new
observables for the seismologists, new types of virtuals seismograms that are not only located at the 
place of earthquakes and that are provided by the operation of correlation  which requires significant computations.
For instance, one can obtain wave paths that probes the deepest part of the Earth.
%(variations in space and time of the seismic waves)

@@

Whisper is one of the projects that have made it possible to ensure that the seismic noise brought new observable.
This permits to carry out several scientific results including imaging and monitoring. 
Concerning monitoring, further studies provide news results about sligth variations of seismics waves induce by earthquakes.
Many articles are in part due to this project \footnote{see whisper.obs.ujf-grenoble.fr, rubric publication} as well as
several post-docs and PhD.

@@

\begin{thebibliography}{9}
\bibitem{key:CCQSC}
 Gen-Tao Chiang, Peter Clapham, Guoying Qi, Kevin Sale and Guy Coates,
 Implementing a genomic data management system using iRODS in the Wellcome Trust Sanger Institute.
{\em BMC Bioinformatics,12(1):361+, September 2011.}
\end{thebibliography}

>>>>

The \emph{Whisper} \footnote{FP7 ERC Advanced grant 227507, see whisper.obs.ujf-grenoble.fr} 
project is a an european project on seismology whose goal is to study properties of the earth
with the seismic ambient noise such that evolution of seismic waves speed. 
This noise is almost all the signal continuously recorded by
the seismic stations worldwide (Europe, China, USA, Japan), except earthquakes. It offers new
observables for the seismologists, new types of virtuals seismograms that are not only located at the 
place of earthquakes and that are provided by the operation of correlation  which requires significant computations.
For instance, one can obtain wave paths that probes the deepest part of the Earth \cite{key:BPCPBR, key:PCP}.
%(variations in space and time of the seismic waves)

@@

Whisper is one of the projects that have made it possible to ensure that the seismic noise brought new observable.
This permits to carry out several scientific results including imaging and monitoring. 
Concerning monitoring, further studies provide news results about sligth variations of seismics waves induce by earthquakes.
Many articles are in part due to this project as well as
several post-docs and PhD (see \cite{key:CFLC2010, key:BPCPBR, key:HCM2014, key:OPLC2013, key:PCP}) and also whisper.obs.ujf-grenoble.fr, rubric publication).

@@

\begin{thebibliography}{9}

\bibitem{key:BPCPBR}
P Bou\'e, P Poli, M Campillo, H Pedersen, X Briand, P Roux,
Teleseismic correlations of ambient seismic noise for deep global imaging of the Earth.
{\em Geophysical Journal International 194 (2), 844-848.}

\bibitem{key:CFLC2010}
JH Chen, B Froment, QY Liu, M Campillo.
Distribution of seismic wave speed changes associated with the 12 May 2008 Mw 7.9 Wenchuan earthquake.
{\em Geophysical Research Letters 37 (18).}

\bibitem{key:CCQSC}
 Gen-Tao Chiang, Peter Clapham, Guoying Qi, Kevin Sale and Guy Coates,
 Implementing a genomic data management system using iRODS in the Wellcome Trust Sanger Institute.
{\em BMC Bioinformatics,12(1):361+, September 2011.}

\bibitem{key:HCM2014}
G. Hillers, M. Campillo, K.-F. Ma.
Seismic velocity variations at TCDP are controlled by MJO driven precipitation pattern and high fluid discharge properties.
{\em Earth and Planetary Science Letters, Volume 391, 1 April 2014, Pages 121-127.}

\bibitem{key:OPLC2013}
Obermann, A., T. Plan\`es, E. Larose, and M. Campillo.
Imaging preeruptive and coeruptive structural and mechanical changes of a volcano with ambient seismic noise.
{\em J. Geophys. Res. Solid Earth, 118, 6285-6294. }

\bibitem{key:PCP}
P. Poli, M. Campillo H. A. Pedersen,
Body-wave imaging of Earth's mantle discontinuities from ambient seismic noise.
{\em Science 338 (6110), 1063-1065.}

\end{thebibliography}
